### 2018-08-29 Sections/network_algorithms.tex
Fixed comment positions

\startnormtable
\begin{table*}[!htbp]
	\begin{tabular}{|c|c|c|c|}
		\hline
  		\rowcolor{Dandelion} Algorithm & Description & Complexity class & Scaling \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Breadth-first-search & Explore all vertices in a graph & \textbf{P} & $O(|V|+|E|)$ \\
  		\hline
  		\rowcolor{LimeGreen} Depth-first-search & (same as above) & \textbf{P} & $O(|V|+|E|)$ \\
		\hline
  		\rowcolor{LimeGreen} Shortest-path (Dijkstra) & Find the shortest route between two nodes & \textbf{P} & $O(|V|^2)$ \\
  		\rowcolor{LimeGreen} & in a directed graph & &  \\
  		  		\hline
		\rowcolor{LimeGreen} Shortest-path (\textit{A*}) & (same as above) & \textbf{P} & (varying) \\
  		  		\hline
		\rowcolor{LimeGreen} Single-source shortest path & Find the shortest paths from a given node to & \textbf{P} & $O(|V|\cdot |E|)$\\
  		\rowcolor{LimeGreen} & \textit{all} other nodes & & \\
 		\hline
		\rowcolor{LimeGreen} Minimum spanning tree & Find a spanning tree of a graph that minimises & \textbf{P} & $O(|E|\log |V|)$ \\
  		\rowcolor{LimeGreen} & the total of the edge weights & & \\
  		\hline
  		\rowcolor{LimeGreen} Minimum cost flow & Minimise total costs in a network &  \textbf{P} & $O(|V|\log |V|(|E|$\\
  		\rowcolor{LimeGreen} (Orlin) & with a specified amount of flow& & $+|V|\log |V|))$ \\
  		\hline
  		\rowcolor{LimeGreen} Maximum flow & Maximise flow in a network, regardless of costs & \textbf{P} & $O(|E|\cdot c_\mathrm{max})$ \\
  		\rowcolor{LimeGreen} (Ford-Fulkerson) & & & \\
  		\hline
  		\rowcolor{Lavender} Multi-commodity flow & Same as maximum flow, but generalised to & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & arbitrary numbers of users & (exactly), & \\
  		\rowcolor{Lavender} & & \textbf{P} (approximation & \\
  		\rowcolor{Lavender} & & using heuristics) & \\
  		\hline
  		\rowcolor{Lavender} Vehicle routing problem & Generalises the shortest-path algorithm to multiple & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & users, with distinct sources and destinations & & \\ 
  		\hline
  		\rowcolor{Lavender} Vehicle rescheduling problem & Same as above but with dynamically changing costs & \textbf{NP}-complete & ? \\
    	\hline
	\end{tabular}
	\caption{Summary of some important network algorithms and their complexities. The \textbf{NP}-complete algorithms are not believed to have efficient classical algorithms, and their exact scaling is not well understood.} \label{tab:net_alg_sum} \index{Network algorithms}\index{Breadth-first-search (BFS) algorithm}\index{Depth-first-search (DFS) algorithm}\index{Shortest-path algorithm}\index{Single-source shortest path algorithm}\index{Minimum spanning tree algorithm}\index{Minimum cost flow algorithm}\index{Maximum flow algorithm}\index{Multi-commodity flow algorithm}\index{Vehicle routing problem}\index{Vehicle rescheduling problem}
\end{table*}
\startalgtable

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[width=0.3\textwidth]{BFS_DFS_long}
	\caption{Comparison of the order in which vertices are explored, using the breadth-first-search (BFS) and depth-first-search (DFS) algorithms, where vertex 1 is the root vertex.} \label{fig:BFS_DFS}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[width=0.65\textwidth]{BFS_DFS}
	\caption{Comparison of the order in which vertices are explored, using the breadth-first-search (BFS) and depth-first-search (DFS) algorithms, where vertex 1 is the root vertex.} \label{fig:BFS_DFS}
	\end{figure*}
\fi

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function DijkstraShortestPath($G$,$A$,$B$):
\begin{enumerate}
	\item currentNode = $A$
    \item tentativeDistances[$A$] = 0
    \item tentativeDistances[others] = $\infty$
    \item nodesVisited[$A$] = True
    \item nodesVisited[others] = False
    \item loopStart:
    \item neighbours = currentNode.neighbourhood
    \item nodesVisited[neighbours] = True
    \item for(n$\in$neighbours) \{
    \setlength{\itemindent}{0.2in}
    \item newTentativeDist = \\ min(tentativeDistances[currentNode] \\+ edgeWeight[currentNode,n],\\
        tentativeDistances[n])\\
    \item nodesVisited[currentNode] = True
    \setlength{\itemindent}{0in}
    \item \}
    \item if(nodesVisited[$B$] = True) \{
    \setlength{\itemindent}{0.2in}
	\item return(tentativeDistances[$B$])
	\item $\Box$
    \setlength{\itemindent}{0in}
    \item \}
	\item currentNode = \\
	tentativeDistances[unvisitedNodes].\\
	nodeWithSmallest()
	\item goto(loop)
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{Dijkstra's original shortest-path algorithm for finding the lowest weight path through a graph, $G$, between two vertices, $A$ (source) and $B$ (destination). The algorithm has $O(|V|^2)$ runtime (in \textbf{P}).} \label{alg:dijkstra}\index{Shortest-path algorithm}
\end{table}

>>>>

\startnormtable
\begin{table*}[!htbp]
	\begin{tabular}{|c|c|c|c|}
		\hline
  		\rowcolor{Dandelion} Algorithm & Description & Complexity class & Scaling \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Breadth-first-search & Explore all vertices in a graph & \textbf{P} & $O(|V|+|E|)$ \\
  		\hline
  		\rowcolor{LimeGreen} Depth-first-search & (same as above) & \textbf{P} & $O(|V|+|E|)$ \\
		\hline
  		\rowcolor{LimeGreen} Shortest-path (Dijkstra) & Find the shortest route between two nodes & \textbf{P} & $O(|V|^2)$ \\
  		\rowcolor{LimeGreen} & in a directed graph & &  \\
  		  		\hline
		\rowcolor{LimeGreen} Shortest-path (\textit{A*}) & (same as above) & \textbf{P} & (varying) \\
  		  		\hline
		\rowcolor{LimeGreen} Single-source shortest path & Find the shortest paths from a given node to & \textbf{P} & $O(|V|\cdot |E|)$\\
  		\rowcolor{LimeGreen} & \textit{all} other nodes & & \\
 		\hline
		\rowcolor{LimeGreen} Minimum spanning tree & Find a spanning tree of a graph that minimises & \textbf{P} & $O(|E|\log |V|)$ \\
  		\rowcolor{LimeGreen} & the total of the edge weights & & \\
  		\hline
  		\rowcolor{LimeGreen} Minimum cost flow & Minimise total costs in a network &  \textbf{P} & $O(|V|\log |V|(|E|$\\
  		\rowcolor{LimeGreen} (Orlin) & with a specified amount of flow& & $+|V|\log |V|))$ \\
  		\hline
  		\rowcolor{LimeGreen} Maximum flow & Maximise flow in a network, regardless of costs & \textbf{P} & $O(|E|\cdot c_\mathrm{max})$ \\
  		\rowcolor{LimeGreen} (Ford-Fulkerson) & & & \\
  		\hline
  		\rowcolor{Lavender} Multi-commodity flow & Same as maximum flow, but generalised to & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & arbitrary numbers of users & (exactly), & \\
  		\rowcolor{Lavender} & & \textbf{P} (approximation & \\
  		\rowcolor{Lavender} & & using heuristics) & \\
  		\hline
  		\rowcolor{Lavender} Vehicle routing problem & Generalises the shortest-path algorithm to multiple & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & users, with distinct sources and destinations & & \\ 
  		\hline
  		\rowcolor{Lavender} Vehicle rescheduling problem & Same as above but with dynamically changing costs & \textbf{NP}-complete & ? \\
    	\hline
	\end{tabular}
	\captionspacealg \caption{Summary of some important network algorithms and their complexities. The \textbf{NP}-complete algorithms are not believed to have efficient classical algorithms, and their exact scaling is not well understood.} \label{tab:net_alg_sum} \index{Network algorithms}\index{Breadth-first-search (BFS) algorithm}\index{Depth-first-search (DFS) algorithm}\index{Shortest-path algorithm}\index{Single-source shortest path algorithm}\index{Minimum spanning tree algorithm}\index{Minimum cost flow algorithm}\index{Maximum flow algorithm}\index{Multi-commodity flow algorithm}\index{Vehicle routing problem}\index{Vehicle rescheduling problem}
\end{table*}
\startalgtable

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[width=0.3\textwidth]{BFS_DFS_long}
	\captionspacefig \caption{Comparison of the order in which vertices are explored, using the breadth-first-search (BFS) and depth-first-search (DFS) algorithms, where vertex 1 is the root vertex.} \label{fig:BFS_DFS}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[width=0.65\textwidth]{BFS_DFS}
	\captionspacefig \caption{Comparison of the order in which vertices are explored, using the breadth-first-search (BFS) and depth-first-search (DFS) algorithms, where vertex 1 is the root vertex.} \label{fig:BFS_DFS}
	\end{figure*}
\fi

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function DijkstraShortestPath($G$,$A$,$B$):
\begin{enumerate}
	\item currentNode = $A$
    \item tentativeDistances[$A$] = 0
    \item tentativeDistances[others] = $\infty$
    \item nodesVisited[$A$] = True
    \item nodesVisited[others] = False
    \item loopStart:
    \item neighbours = currentNode.neighbourhood
    \item nodesVisited[neighbours] = True
    \item for(n$\in$neighbours) \{
    \setlength{\itemindent}{0.2in}
    \item newTentativeDist = \\ min(tentativeDistances[currentNode] \\+ edgeWeight[currentNode,n],\\
        tentativeDistances[n])\\
    \item nodesVisited[currentNode] = True
    \setlength{\itemindent}{0in}
    \item \}
    \item if(nodesVisited[$B$] = True) \{
    \setlength{\itemindent}{0.2in}
	\item return(tentativeDistances[$B$])
	\item $\Box$
    \setlength{\itemindent}{0in}
    \item \}
	\item currentNode = \\
	tentativeDistances[unvisitedNodes].\\
	nodeWithSmallest()
	\item goto(loop)
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{Dijkstra's original shortest-path algorithm for finding the lowest weight path through a graph, $G$, between two vertices, $A$ (source) and $B$ (destination). The algorithm has $O(|V|^2)$ runtime (in \textbf{P}).} \label{alg:dijkstra}\index{Shortest-path algorithm}
\end{table}

### 2018-08-29 Sections/optical_routers.tex
Fixed comment positions

\startnormtable
\begin{table*}[!htbp]
	\begin{tabular}{|c|c|c|}
		\hline
  		Device & Resource requirements & Optical depth \\
  		\hline
  		\hline
  		Two-channel two-port switch & \mbox{$N_\mathrm{bs}=2$}, \mbox{$N_\mathrm{ps}=1$} & \mbox{$d=1$} \\
  		Linear $n$-port multiplexer & \mbox{$N_\mathrm{s}=n-1$} & \mbox{$1\leq d\leq n-1$} \\
  		Pyramid $n$-port multiplexer & \mbox{$N_\mathrm{s}=n-1$} & \mbox{$d=\log_2(n)$} \\
    	Single-channel multi-port switch (linear) & \mbox{$N_\mathrm{s}=2n-3$} & \mbox{$2\leq d\leq 2n-3$} \\
  		Single-channel multi-port switch (pyramid) & \mbox{$N_\mathrm{s}=2n-3$} & \mbox{$d=2\,\log_2(n)-1$} \\
  		Multi-channel multi-port switch & \mbox{$N_\mathrm{s} = \left\lceil \frac{n^2}{2}\right\rceil - n + 1$} & \mbox{$\left\lceil \frac{n}{2} \right\rceil \leq d\leq n-1$} \\
  		Crossbar switch & \mbox{$N_\mathrm{s}=n^2$} & \mbox{$1\leq d\leq 2n-1$}\\
    	\hline
	\end{tabular}
	\captionspace \caption{Summary of different primitives for constructing optical routers. $n$, $N_\mathrm{bs}$, $N_\mathrm{ps}$ and $N_\mathrm{s}$ are the number of input/output ports, beamsplitters, phase-shifters, and two-port switches respectively. $d$ is the optical depth (in units of number of two-port switches). Since all of the multi-port devices are constructed from two-port switches, in all cases \mbox{$N_\mathrm{bs} = 2 N_\mathrm{s}$} and \mbox{$N_\mathrm{ps} = N_\mathrm{s}$}.} \label{tab:router_summary} \index{Optical routers}\index{Optical depth}\index{Router resource requirements}
\end{table*}
\startalgtable

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{two_channel_two_port_switch}
\captionspace \caption{(top) A two-channel two-port switch has two inputs and two outputs, implementing either an identity or swap operation between them. This may be constructed using a Mach-Zehnder interferometer with a variable, classically-controlled phase-shift, $e^{i\phi}$, in one of the arms, which may be implemented using an acousto-optic or electro-optic modulator (AOM or EOM). The phase-shift is allowed to be either \mbox{$\phi=0$} for an identity channel (bottom left) or \mbox{$\phi=\pi$} for a swap operation (bottom right). Because the switch is based on MZ interference, this technique only applies to optical states which undergo MZ interference. The total resource requirements are two 50:50 beamsplitters and a single phase-shifter.} \label{fig:two_channel_two_port_switch} \index{Two-channel two-port switches}\index{Mach-Zehnder (MZ) interference}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.425\textwidth]{linear_multiplexer}
\captionspace \caption{Linear multiplexers (left) and demultiplexers (right) may be constructed from a linear chain of two-port switches (grey boxes), cascading into one another. These switch a single optical channel between $n$ ports. The total resource requirements are \mbox{$n-1$} two-port switches. The optical depth ranges from $1$ (for the first port) to \mbox{$n-1$} (for the final port).} \label{fig:linear_multiplexer} \index{Linear multiplexers \& demultiplexers}
\end{figure}

\begin{figure}[!htbp]
\includegraphics[width=0.35\textwidth]{pyramid_multiplexer}
\captionspace \caption{Pyramid multiplexers (top) and demultiplexers (bottom) decompose the multiplexing into a binary tree-structure of two-port switches (grey boxes), shown here for the case of \mbox{$n=8$} ports. For $n$ ports, all optical paths observe an optical depth of \mbox{$d=\log_2(n)$} two-port switches, of which there are \mbox{$n-1$} in total.} \label{fig:pyramid_multiplexer} \index{Pyramid multiplexers \& demultiplexers}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.375\textwidth]{single_channel_multi_port_switch}
\captionspace \caption{A single-channel multi-port switch may be constructed by demultiplexing the $n$ input ports to a single port, routing the desired input channel to that port, before multiplexing it back out to the desired output port. This allows an arbitrary input to be routed to an arbitrary output, but only one channel at a time. This requires \mbox{$2n-3$} two-port switches in total.} \label{fig:single_channel_multi_port_switch} \index{Single-channel multi-port switches}	
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{multi_channel_multi_port_switch}
\captionspace \caption{A completely general multi-channel multi-port switch may be constructed using a staggered grid of two-port switches (grey boxes), shown here for \mbox{$n=6$} ports. This allows the implementation of an arbitrary permutation between input and output ports, enabling all $n$ channels to be simultaneously utilised and routed across distinct input-to-output routes. This requires \mbox{$\left\lceil \frac{n^2}{2}\right\rceil - n + 1$} two-port switches in total. Optical depth is approximately equal across all input-to-output paths.} \label{fig:multi_channel_multi_port_switch} \index{Multi-channel multi-port switches}	
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.4\textwidth]{crossbar_switch}
\captionspace \caption{Crossbar architecture for multi-port switching. Each orange box represents a \mbox{$2\times 2$} switch, of any physical implementation. The switching sequence of the constituent two-port switches is defined by a binary \mbox{$n\times n$} permutation matrix, whose elements determine whether a given two-port switch flips modes or doesn't.} \label{fig:crossbar_switch}	
\end{figure}

\begin{figure}[!htbp]
\includegraphics[width=0.4\textwidth]{crossbar_example}
\captionspace \caption{Example switching configuration for a \mbox{$5\times 5$} crossbar switch. The switch colours represent whether the respective \mbox{$2\times 2$} switch is set to flip (red) the modes or not (orange).} \label{fig:crossbar_example}	
\end{figure}

>>>>

\startnormtable
\begin{table*}[!htbp]
	\begin{tabular}{|c|c|c|}
		\hline
  		Device & Resource requirements & Optical depth \\
  		\hline
  		\hline
  		Two-channel two-port switch & \mbox{$N_\mathrm{bs}=2$}, \mbox{$N_\mathrm{ps}=1$} & \mbox{$d=1$} \\
  		Linear $n$-port multiplexer & \mbox{$N_\mathrm{s}=n-1$} & \mbox{$1\leq d\leq n-1$} \\
  		Pyramid $n$-port multiplexer & \mbox{$N_\mathrm{s}=n-1$} & \mbox{$d=\log_2(n)$} \\
    	Single-channel multi-port switch (linear) & \mbox{$N_\mathrm{s}=2n-3$} & \mbox{$2\leq d\leq 2n-3$} \\
  		Single-channel multi-port switch (pyramid) & \mbox{$N_\mathrm{s}=2n-3$} & \mbox{$d=2\,\log_2(n)-1$} \\
  		Multi-channel multi-port switch & \mbox{$N_\mathrm{s} = \left\lceil \frac{n^2}{2}\right\rceil - n + 1$} & \mbox{$\left\lceil \frac{n}{2} \right\rceil \leq d\leq n-1$} \\
  		Crossbar switch & \mbox{$N_\mathrm{s}=n^2$} & \mbox{$1\leq d\leq 2n-1$}\\
    	\hline
	\end{tabular}
	\captionspacealg \caption{Summary of different primitives for constructing optical routers. $n$, $N_\mathrm{bs}$, $N_\mathrm{ps}$ and $N_\mathrm{s}$ are the number of input/output ports, beamsplitters, phase-shifters, and two-port switches respectively. $d$ is the optical depth (in units of number of two-port switches). Since all of the multi-port devices are constructed from two-port switches, in all cases \mbox{$N_\mathrm{bs} = 2 N_\mathrm{s}$} and \mbox{$N_\mathrm{ps} = N_\mathrm{s}$}.} \label{tab:router_summary} \index{Optical routers}\index{Optical depth}\index{Router resource requirements}
\end{table*}
\startalgtable

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{two_channel_two_port_switch}
\captionspacefig \caption{(top) A two-channel two-port switch has two inputs and two outputs, implementing either an identity or swap operation between them. This may be constructed using a Mach-Zehnder interferometer with a variable, classically-controlled phase-shift, $e^{i\phi}$, in one of the arms, which may be implemented using an acousto-optic or electro-optic modulator (AOM or EOM). The phase-shift is allowed to be either \mbox{$\phi=0$} for an identity channel (bottom left) or \mbox{$\phi=\pi$} for a swap operation (bottom right). Because the switch is based on MZ interference, this technique only applies to optical states which undergo MZ interference. The total resource requirements are two 50:50 beamsplitters and a single phase-shifter.} \label{fig:two_channel_two_port_switch} \index{Two-channel two-port switches}\index{Mach-Zehnder (MZ) interference}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.425\textwidth]{linear_multiplexer}
\captionspacefig \caption{Linear multiplexers (left) and demultiplexers (right) may be constructed from a linear chain of two-port switches (grey boxes), cascading into one another. These switch a single optical channel between $n$ ports. The total resource requirements are \mbox{$n-1$} two-port switches. The optical depth ranges from $1$ (for the first port) to \mbox{$n-1$} (for the final port).} \label{fig:linear_multiplexer} \index{Linear multiplexers \& demultiplexers}
\end{figure}

\begin{figure}[!htbp]
\includegraphics[width=0.35\textwidth]{pyramid_multiplexer}
\captionspacefig \caption{Pyramid multiplexers (top) and demultiplexers (bottom) decompose the multiplexing into a binary tree-structure of two-port switches (grey boxes), shown here for the case of \mbox{$n=8$} ports. For $n$ ports, all optical paths observe an optical depth of \mbox{$d=\log_2(n)$} two-port switches, of which there are \mbox{$n-1$} in total.} \label{fig:pyramid_multiplexer} \index{Pyramid multiplexers \& demultiplexers}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.375\textwidth]{single_channel_multi_port_switch}
\captionspacefig \caption{A single-channel multi-port switch may be constructed by demultiplexing the $n$ input ports to a single port, routing the desired input channel to that port, before multiplexing it back out to the desired output port. This allows an arbitrary input to be routed to an arbitrary output, but only one channel at a time. This requires \mbox{$2n-3$} two-port switches in total.} \label{fig:single_channel_multi_port_switch} \index{Single-channel multi-port switches}	
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{multi_channel_multi_port_switch}
\captionspacefig \caption{A completely general multi-channel multi-port switch may be constructed using a staggered grid of two-port switches (grey boxes), shown here for \mbox{$n=6$} ports. This allows the implementation of an arbitrary permutation between input and output ports, enabling all $n$ channels to be simultaneously utilised and routed across distinct input-to-output routes. This requires \mbox{$\left\lceil \frac{n^2}{2}\right\rceil - n + 1$} two-port switches in total. Optical depth is approximately equal across all input-to-output paths.} \label{fig:multi_channel_multi_port_switch} \index{Multi-channel multi-port switches}	
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.4\textwidth]{crossbar_switch}
\captionspacefig \caption{Crossbar architecture for multi-port switching. Each orange box represents a \mbox{$2\times 2$} switch, of any physical implementation. The switching sequence of the constituent two-port switches is defined by a binary \mbox{$n\times n$} permutation matrix, whose elements determine whether a given two-port switch flips modes or doesn't.} \label{fig:crossbar_switch}	
\end{figure}

\begin{figure}[!htbp]
\includegraphics[width=0.4\textwidth]{crossbar_example}
\captionspacefig \caption{Example switching configuration for a \mbox{$5\times 5$} crossbar switch. The switch colours represent whether the respective \mbox{$2\times 2$} switch is set to flip (red) the modes or not (orange).} \label{fig:crossbar_example}	
\end{figure}

### 2018-08-29 Sections/optical_stability_in_quantum_networks.tex
Fixed comment positions

\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{wavepacket} \\
	\captionspace \caption{(top) A photonic wave-packet of the form of Eq.~(\ref{eq:wavepacket_modulated}), with Gaussian temporal envelope of width $\sigma$ (orange), shifted by a carrier frequency $\omega_0$ (blue).} \label{fig:HOM_vs_MZ}
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{MZ_setup} \\
	\includegraphics[width=0.475\textwidth]{MZ}
	\captionspace \caption{Mach-Zehnder self-interference of a single photon. (top) Layout of the interferometer. The photon is subject to a time-delay $\tau$ within only the upper arm of a balanced interferometer, comprising two 50:50 beamsplitters. (bottom) Interference fringe $P_\mathrm{MZ}(\tau)$ as a function of the time-delay. The interference is sensitive at the scale of the photon wavelength, (blue) in Fig.~\ref{fig:HOM_vs_MZ}.} \label{fig:MZ_inter}
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.325\textwidth]{HOM_setup} \\
	\includegraphics[width=0.475\textwidth]{HOM}
	\captionspace \caption{Hong-Ou-Mandel interference between two independent photons, $A$ and $B$. (top) Layout of the interferometer. Two photons given by mode operators $\hat{A}^\dag$ and $\hat{B}^\dag$\index{Mode operators} (Sec.~\ref{sec:spatio_temporal}), both with temporal distribution function $\psi(t)$, interfere at a 50:50 beamsplitter, where mode $A$ is first subject to a time-delay $\tau$. (bottom) Interference fringe $P_\mathrm{HOM}(\tau)$ as a function of the time-delay. The fringe is only sensitive at the scale of the wave-packet envelope, (orange) in Fig.~\ref{fig:HOM_vs_MZ}.} \label{fig:HOM_inter}
\end{figure}

@@

\startnormtable
\begin{table}[!htbp]
	\begin{tabular}{|c|c|}
		\hline
  		\rowcolor{Dandelion} Protocol & Interference type \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Cluster state measurement & None \\
   		\rowcolor{LimeGreen} Quantum anonymous broadcasting & None \\
  		\rowcolor{LimeGreen} QKD (BB84, E91) & None \\
  		\rowcolor{LimeGreen} Quantum memory & None \\
  		\rowcolor{LimeGreen} Quantum process tomography & None \\
  		\rowcolor{LimeGreen} Quantum state tomography & None \\
  		\rowcolor{LimeGreen} Random number generation & None \\
  		\rowcolor{LimeGreen} Separable measurements & None \\
  		\rowcolor{LimeGreen} Separable state preparation & None \\
  		\rowcolor{LimeGreen} Optical interfacing & None \\
  		\hline
  		\rowcolor{Apricot} Cluster state preparation (fusion gates) & HOM \\
  		\rowcolor{Apricot} Entanglement purification & HOM \\
  		\rowcolor{Apricot} Entanglement swapping & HOM \\ 
  		\rowcolor{Apricot} Matter qubit entangling operations & HOM \\
  		\rowcolor{Apricot} Partial Bell state measurements & HOM \\
   		\rowcolor{Apricot} Quantum gate teleportation & HOM \\
  		\rowcolor{Apricot} Quantum state teleportation & HOM \\
  		\rowcolor{Apricot} Superdense coding & HOM \\
  		\hline
  		\rowcolor{Lavender} \textsc{BosonSampling} & MZ \\
  		\rowcolor{Lavender} General linear optics networks & MZ \\
  		\rowcolor{Lavender} Universal LOQC (KLM) & MZ \\
  		\rowcolor{Lavender} Quantum metrology & MZ \\
  		\rowcolor{Lavender} Quantum walks & MZ \\
    	\hline
	\end{tabular}
	\captionspace \caption{Summary of the major quantum network protocols presented in Sec.~\ref{sec:protocols_quant_int}, and their required type of interference.}\index{Interferometric requirements}\label{table:summary_inter}
\end{table}

>>>>

\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{wavepacket} \\
	\captionspacefig \caption{(top) A photonic wave-packet of the form of Eq.~(\ref{eq:wavepacket_modulated}), with Gaussian temporal envelope of width $\sigma$ (orange), shifted by a carrier frequency $\omega_0$ (blue).} \label{fig:HOM_vs_MZ}
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{MZ_setup} \\
	\includegraphics[width=0.475\textwidth]{MZ}
	\captionspacefig \caption{Mach-Zehnder self-interference of a single photon. (top) Layout of the interferometer. The photon is subject to a time-delay $\tau$ within only the upper arm of a balanced interferometer, comprising two 50:50 beamsplitters. (bottom) Interference fringe $P_\mathrm{MZ}(\tau)$ as a function of the time-delay. The interference is sensitive at the scale of the photon wavelength, (blue) in Fig.~\ref{fig:HOM_vs_MZ}.} \label{fig:MZ_inter}
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.325\textwidth]{HOM_setup} \\
	\includegraphics[width=0.475\textwidth]{HOM}
	\captionspacefig \caption{Hong-Ou-Mandel interference between two independent photons, $A$ and $B$. (top) Layout of the interferometer. Two photons given by mode operators $\hat{A}^\dag$ and $\hat{B}^\dag$\index{Mode operators} (Sec.~\ref{sec:spatio_temporal}), both with temporal distribution function $\psi(t)$, interfere at a 50:50 beamsplitter, where mode $A$ is first subject to a time-delay $\tau$. (bottom) Interference fringe $P_\mathrm{HOM}(\tau)$ as a function of the time-delay. The fringe is only sensitive at the scale of the wave-packet envelope, (orange) in Fig.~\ref{fig:HOM_vs_MZ}.} \label{fig:HOM_inter}
\end{figure}

@@

\startnormtable
\begin{table}[!htbp]
	\begin{tabular}{|c|c|}
		\hline
  		\rowcolor{Dandelion} Protocol & Interference type \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Cluster state measurement & None \\
   		\rowcolor{LimeGreen} Quantum anonymous broadcasting & None \\
  		\rowcolor{LimeGreen} QKD (BB84, E91) & None \\
  		\rowcolor{LimeGreen} Quantum memory & None \\
  		\rowcolor{LimeGreen} Quantum process tomography & None \\
  		\rowcolor{LimeGreen} Quantum state tomography & None \\
  		\rowcolor{LimeGreen} Random number generation & None \\
  		\rowcolor{LimeGreen} Separable measurements & None \\
  		\rowcolor{LimeGreen} Separable state preparation & None \\
  		\rowcolor{LimeGreen} Optical interfacing & None \\
  		\hline
  		\rowcolor{Apricot} Cluster state preparation (fusion gates) & HOM \\
  		\rowcolor{Apricot} Entanglement purification & HOM \\
  		\rowcolor{Apricot} Entanglement swapping & HOM \\ 
  		\rowcolor{Apricot} Matter qubit entangling operations & HOM \\
  		\rowcolor{Apricot} Partial Bell state measurements & HOM \\
   		\rowcolor{Apricot} Quantum gate teleportation & HOM \\
  		\rowcolor{Apricot} Quantum state teleportation & HOM \\
  		\rowcolor{Apricot} Superdense coding & HOM \\
  		\hline
  		\rowcolor{Lavender} \textsc{BosonSampling} & MZ \\
  		\rowcolor{Lavender} General linear optics networks & MZ \\
  		\rowcolor{Lavender} Universal LOQC (KLM) & MZ \\
  		\rowcolor{Lavender} Quantum metrology & MZ \\
  		\rowcolor{Lavender} Quantum walks & MZ \\
    	\hline
	\end{tabular}
	\captionspacealg \caption{Summary of the major quantum network protocols presented in Sec.~\ref{sec:protocols_quant_int}, and their required type of interference.}\index{Interferometric requirements}\label{table:summary_inter}
\end{table}
